Ornaments as indicators of social changes in northeastern Taiwan before and after the European colonial period

### 2020-05-15 analysis/paper/paper.Rmd
fixed one missing in-text citation
revision submitted to ARA

ggsave(plot = kwl_ages_curve,
       here("analysis", "figures",
       "plot-c14-ages-distribution.jpg"),
       width = 120, 
       dpi = 300,
       height = 60,
       units = "mm")

@@

We would like to thank the Yilan County Cultural Affairs Bureau in Taiwan for permitting access to the ornaments used in this study. We thank Shui-jin Chiu, Shu-hui Jian, Jiun-yao Lai, and the staff in archaeology lab for their invaluable assistance in preparing samples for analysis. We also thank Yu-pei Chen for the discussion regarding the site at the earliest stage of fieldwork. This work was supported in part by the Chester Fritz Graduate Fellowship and travel grants from the Department of Anthropology at University of Washington. We would also like to thank Ben Fitzhugh and Peter Lape for their insightful comments on an early draft.

>>>>

ggsave(plot = kwl_ages_curve,
       here("analysis", "figures",
       "plot-c14-ages-distribution.jpg"),
       width = 120, 
       dpi = 300,
       height = 62,
       units = "mm")

@@

We would like to thank the Yilan County Cultural Affairs Bureau in Taiwan for permitting access to the ornaments used in this study. We thank Shui-jin Chiu, Shu-hui Jian, Jiun-yao Lai, and the staff in archaeology lab for their invaluable assistance in preparing samples for analysis. We also thank Yu-pei Chen for the discussion regarding the site at the earliest stage of fieldwork. This work was supported in part by the Chester Fritz Graduate Fellowship and travel grants from the Department of Anthropology at University of Washington. We thank Ben Fitzhugh and Peter Lape for their insightful comments on an early draft. We also acknowledge comments from anonymous reviewers that have greatly improved this manuscript.
